Constructing the transition graphs of interacting hysterons

### 2022-06-13 Paper_draft.tex
Corrected inconsistency in notation of switching fields

where $s_i \in \{0, 1\}$ are the phases of individual hysterons. We then model the response of individual hysterons to an external driving field $U$ by defining up and down switching fields $u_i^+$ and $u_i^-$. A hysteron transitions from phase 0 to 1 ('up') if $U \geq u_i^+$, and from phase 1 to 0 ('down') if $U \leq u_i^-$.\\
If the system of hysterons is non-interacting, then the switching fields $\{u_i^+\}, \{u_i^-\}$ are fixed values $u_i^{+, -}$. We refer to these switching fields in the absence of interactions as the bare switching fields. If there are interactions, the switching fields are modified by the state $S$:

>>>>

where $s_i \in \{0, 1\}$ are the phases of individual hysterons. We then model the response of individual hysterons to an external driving field $U$ by defining up and down switching fields $U_i^+$ and $U_i^-$. A hysteron transitions from phase 0 to 1 ('up') if $U \geq U_i^+$, and from phase 1 to 0 ('down') if $U \leq U_i^-$.\\
If the system of hysterons is non-interacting, then the switching fields $\{U_i^+\}, \{U_i^-\}$ are fixed values $u_i^{+, -}$. We refer to these switching fields in the absence of interactions as the bare switching fields. If there are interactions, the switching fields are modified by the state $S$:
